Analysis of split plot design using MCMCglmm

### 2017-08-25 README.Rmd
Update README
Correct repository references

# rice.awd.shb

The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.

@@

**Project PI:** Dr. Adam H Sparks  and Dr. Buyung AR Hadi

>>>>

# rice.awd.pests

The goal of _rice.awd.pests_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.

@@

**Project PI:** Dr. Adam H Sparks
